\section{Quality and testing}\label{sec:quality}

I want to take pride in what I do.
Therefore,
I took extra care when I created Notipie
to account for the quality of the product.
I defined the quality as follows:

\begin{itemize}
  \item sufficient product success;
  \item sufficient product reliability; and
  \item sufficient product maintainability and developer satisfaction.
\end{itemize}

I also defined success as:

\begin{itemize}
  \item sufficient correctness of the delivered information;
  \item sufficient usefulness of the delivered information; and
  \item clear presentation of the information.
\end{itemize}

I did not define success in the commercial terms,
because that was not the scope of my project.
I managed to keep my focus on quality,
and keep the list of features in check
by defining an \ac{MVP}.

Every time I added something to the application,
I ran automated integration test suite
(appendix~\ref{apx:integration-test-core})
in order to check if the application quality
did not deteriorate.
I made sure to run the test suite as often as I could
by making it performant.
And so, one integration test run takes 170 milliseconds in total,
as depicted in listing~\ref{lst:integration-test-run}.
The whole automated test suite ran on every change
pushed to Github servers to ensure the solution quality.
I also double-checked the correct behavior
of my application with manual \ac{E2E} tests.

\input{section/quality/minimum-viable-product.tex}
\input{section/quality/e2e-testing.tex}
\input{section/quality/code-quality.tex}
