\section{Conclusion}\label{sec:conclusion}

In this thesis,
I have shown how I defined the problem domain,
solved the project management,
developed the system,
and ensured excellent quality.
Notification management is a topic
that was tackled many times before.
There are more and less sophisticated
project for that,
and Notipie is one more example of them.
However,
with how simple it is to set up,
its simplicity and extendability,
I believe it has its place
in the vast field of
presenting just the right notifications
to its users.

The project itself presented a great opportunity
for exploration of different programming techniques,
experimentation with many approaches to common problems,
and even developing my own,
against what is the most popular in the industry.
In spite of project management
not being a task I anticipated
in a single-developer project,
I am very satisfied with the knowledge
I gained while managing myself.
I started the project over one and a half years ago,
and after all this time, I produced something
I can say I am proud of.

I am very pleased with the \ac{TDD} and \ac{DDD} approaches.
I see them as extremely valuable,
and I plan to use them extensively
in my work from now on.
I am very grateful for the insight
and experience of all the authors of the books,
blog posts, and documentation I read.
I am also appreciative for the enormous amount of work
put by many great people into
the free and open-source software
I used and studied.
I believe that Notipie has a huge potential
to be a successful solution for many
notification management scenarios,
both commercially
and in terms of quality.
